---
title: "Water Trend Peer Review"
author: "Jonie"
date: '2017-07-28'
output:
  ioslides_presentation: default
  slidy_presentation: default
---
##Introduction
</br>
WFO: WFO would be used for equipment cleaning and handwashing.

</br>
This trend Analysis would review the data weekly.

***
###Plot | WFO Generation System

If there's an break for alert or action limit lines, it indicates that the new alert and action is effectived on the date of the break location. A new alert and action limit line can be displayed only after NLT 2 points after limit changing are collected.

```{r, echo=FALSE,results="markup",out.height=470}
library(openxlsx)
source("~/Instance/1_Reproduceable & Repeatable Report/b.trend3.2.2_foregoa.R")
td<-read.xlsx("~/Instance/Data/Data Demo.xlsx","WFO-Data-Input",detectDates=T)

td$Alert<-as.numeric(as.character(td$Alert))
td$Action<-as.numeric(as.character(td$Action))
b.trend(trend_result=td$Result,trend_date=td$Date,trend_room=NA,trend_point=td$Point,trend_alert=td$Alert,trend_action=td$Action,days=360,point.choose=NA,limit=T,add=T,t.title="WFO Trend Chart")
```

***
###Plot | PW-TAMC
```{r, echo=FALSE,results="markup",out.height=470}
library(openxlsx)
source("~/Instance/1_Reproduceable & Repeatable Report/b.trend3.2.2_foregoa.R")
td<-read.xlsx("~/Instance/Data/Data Demo.xlsx",sheet="PW-TAMC-Input",detectDates=T)
td$Alert<-as.numeric(as.character(td$Alert))
td$Action<-as.numeric(as.character(td$Action))
b.trend(trend_result=td$Result,trend_date=td$Date,trend_room=NA,trend_point=td$Point,trend_alert=td$Alert,trend_action=td$Action,days=360,point.choose=NA,limit=T,add=T,t.title="PW TAMC Trend Chart")
```

***
###Plot | PW-Conductivity
```{r, echo=FALSE,results="markup",out.height=470}
library(openxlsx)
source("~/Instance/1_Reproduceable & Repeatable Report/b.trend3.2.2_foregoa.R")
td<-read.xlsx("~/Instance/Data/Data Demo.xlsx",sheet="PW-Conductivity-Input",detectDates=T)
td$Alert<-as.numeric(as.character(td$Alert))
td$Action<-as.numeric(as.character(td$Action))
b.trend(trend_result=td$Result,trend_date=td$Date,trend_room=NA,trend_point=td$Point,trend_alert=td$Alert,trend_action=td$Action,days=360,point.choose=NA,limit=T,add=T,t.title="PW Conductitivy Trend Chart")
```

***
###Plot | PW-TOC
```{r, echo=FALSE,results="markup",out.height=470}
library(openxlsx)
source("~/Instance/1_Reproduceable & Repeatable Report/b.trend3.2.2_foregoa.R")
td<-read.xlsx("~/Instance/Data/Data Demo.xlsx",sheet="PW-TOC-Input",detectDates=T)

td$Alert<-as.numeric(as.character(td$Alert))
td$Action<-as.numeric(as.character(td$Action))
b.trend(trend_result=td$Result,trend_date=td$Date,trend_room=NA,trend_point=td$Point,trend_alert=td$Alert,trend_action=td$Action,days=360,point.choose=NA,limit=T,add=T,t.title="PW TOC Trend Chart")
```